\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    {\Huge \textbf{Nguyen Huu Thang}} \\[6pt]
    {\large \textbf{Software Engineer Intern}} \\[10pt]

    Email: \href{mailto:nhthang312@gmail.com}{nhthang312@gmail.com}
    \ $|$\ 
    Phone: +84 84993 3375
    \\ 
    GitHub: \href{https://github.com/InfinityZero3000}{InfinityZero3000}
    \ $|$\ 
    Portfolio: \href{https://portfolio-infinity-zero.vercel.app/}{portfolio-infinity-zero.vercel.app}
\end{center}

%-----------CAREER OBJECTIVE----------
\section{Career Objective}
Software Engineering student with hands-on experience building web applications with ASP.NET Core, PostgreSQL, and Docker. Implemented authentication/authorization, checkout and payment flows, and production-oriented practices such as structured logging, rate limiting, and health checks. Seeking a Software Engineer Intern role to learn real-world engineering workflows and contribute to shipped features.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ho Chi Minh City University of Industry and Trade (HUIT)}{Ho Chi Minh City, VN}
      {Bachelor of Information Technology; Major: Software Engineering; GPA: 2.94/4.0}{Sep 2023 -- Present}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: Python, SQL, C\#, C++, HTML/CSS}
    }
    \item{
     \textbf{Technologies/Frameworks}{: ASP.NET Core (MVC), Entity Framework Core, REST-style endpoints}
    }
    \item{
     \textbf{Tools \& Others}{: Git/GitHub, Docker, Postman, PostgreSQL, SQL Server, Serilog}
    }
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {John Henry – E-commerce Platform}
      {GitHub: \href{https://github.com/InfinityZero3000/John-Henry-Fashion}{Link} $|$ Live: \href{https://johnhenry-web.onrender.com}{Link}}
      {Web Application | ASP.NET Core 9.0, PostgreSQL, Docker}
      {Web Development}
        \resumeItemListStart
          \resumeItem{Backend Architecture}{
            Built backend controllers and data access for product, cart, checkout, and order domains using ASP.NET Core and EF Core (PostgreSQL). Implemented inventory fields and order status transitions, and used EF Core transactions for multi-step admin updates.
          }
          \resumeItem{Authorization \& Business Logic}{
            Implemented role-based access control (Admin/Seller/Customer) and admin workflows for sales monitoring and system configuration.
          }
          \resumeItem{Payment Integration}{
            Integrated VNPay checkout by generating signed payment URLs (HMAC-SHA512) and handling return callbacks to update payment/order status. Implemented pricing rules including coupons, shipping fee calculation, and order state transitions.
          }
          \resumeItem{Security \& Production}{
            Implemented Google OAuth 2.0 login with ASP.NET Core Identity and BCrypt password hashing, API rate limiting, and audit logging for admin actions/security events. Deployed the containerized application to Render with health checks and Serilog structured logging (optional Redis distributed cache).
          }
    \resumeItemListEnd
    
    \resumeSubheading
      {Hybrid CNN-CBAM-ViT for Skin Cancer Classification}{GitHub: \href{https://github.com/InfinityZero3000/Skincancer_classification}{Link}}
      {Research Project | Python, TensorFlow, Computer Vision}{Deep Learning / Computer Vision}
      \resumeItemListStart
        \resumeItem{Novel Architecture}{Developed a hybrid model combining CNN (local features), CBAM (spatial/channel attention), and Vision Transformer (ViT) for global context.}
        \resumeItem{Performance}{Achieved \textbf{92.49\% F1-score} and \textbf{92.65\% accuracy} on ISIC validation datasets.}
        \resumeItem{Generalization}{Tested on clinical image datasets with sustained \textbf{70\%+} average accuracy, outperforming baseline CNN models.}
            \resumeItem{Contribution}{Iterated on the attention-enhanced pipeline and evaluation workflow to reduce false negatives and improve early-stage diagnosis support.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACTIVITIES-----------------
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Data Science Challenge Finalist}{
  Participated in a Data Science competition project that reached the final round. Contributed to data preprocessing, feature analysis, and model evaluation, and presented the project approach and results to the judges. Certificate: \href{https://raw.githubusercontent.com/InfinityZero3000/Portfolio_zero/refs/heads/main/public/Data-Science-Certificate.png}{Link}}
    \resumeSubItem{Research Member}{Aspect-Based Sentiment Analysis using Knowledge Graphs. University-Level Project (Jul 2025 – Jun 2026)}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
